PeerMind

### 2016-12-03 paper.tex
stash local changes

\title{PeerMind: Towards Collective Decision-Making}

@@

Two of the most shocking democratic votes in recent history occurred in 2016:
The referendum vote for Britain to leave the European Union (``Brexit'') and the election of Donald Trump as
President of the United States.
Both votes were decided by the slimmest of margins, but more significantly, both votes had poor turnout.
We often hear that the Achilles heel of a democracy is low engagement, but this is a fallacy~---~in fact, our goal
should be to decrease engagement.
The ideal governance system is one where citizens do not have to be constantly involved, but the system is still
acting as the citizens would like it to. Can we increase legitimacy within a democracy while also decreasing the
attention required at the same time?

In this paper we present our work on improving the collective decision-making through use of a web application
to facilitate the process.
In contrast with existing similar solutions, our web application integrates new ideas in how to improve this process:
use of range voting, dynamic quorum, and vote delegation.
The broad idea is that instead of just trying to move the voting process online~---~something many others have done
previously~---~we in fact wish to add value by voting online.
Specifically, we can compute results faster, more accurately,
%and securely,
we can use sophisticated statistics to
estimate important quantities for the entire voting population, we can allow for members to entrust others who have
more expertise on topics than they do themselves, and we can promote clarity and full understanding of the voting
items for all.

%The broad idea is that instead of just trying to move the voting process online -- something many others do -- we in
%fact add additional value by voting online.
%Specifically, we can compute results faster and more accurately, we can use sophisticated statistics to estimate
%quantities for the entire voting population, and we can promote clarity and full understanding of the voting items for all.
%
%\todo[inline]{Main questions and answers follow.}
%
%What problem are we solving? Why is it important to solve? What is the story?
%
%Finding a way to lower attention required but increase legitimacy of democratic decisions.
%Traditionally legitimacy is increased by increasing participation/attention required.
%It is an everlasting problem.
%How to outsource governance and at the same time assure it does not get corrupt
%or tyrannic.
%
%Has anyone else tried to solve it or related problems? How did they try
%and what were the results (subjective or objective)?
%
%Described here: \url{http://mitar.tnode.com/post/73983101095/peer-to-peer-voting-scheme}.
%Some tried delegations, but mostly only to one person.
%Getting issues that you have tree-structure with possible cycles you cannot resolve.
%Often there were reported UI problems as well.
%So just technically improving is not enough, you also have to have UI for the technical solution so that people can trust.
%
%How are you solving the problem? What technologies are you using?
%
%Using dynamic quorum, score voting, delegation, and nice integration with UI/UX.
%
%How will you know how well you solved the problem? How will those technologies address the issues?
%
%If it improves decision making, participation, inclusivity, activity of people engaged in decision making in my house.
%So currently we have issues with reaching the quorum and many people do not participate.
%I would like for them to have easier time participating (less time required) and as a consequence more people to
%participate collectively.
%If I observe that I think I will know I solved the problem.
%
%\todo[inline]{This rest of the section is mostly notes. Organize and improve.}
%
%We can often hear that the issue of our democracy is low engagement.
%But this is a fallacy, because we should be instead trying to decrease engagement.
%The best governance system is one where you do not have to be involved yourself, but it is still doing things
%like you would like to do them.
%% Or even, doing things you might not even know that you would like to be done, especially in a long term.
%We want to outsource the job of coordination between people.
%Sometimes you want to coordinate people yourself (in your company, team), you might enjoy it, but in most cases
%you cannot or do not want to, so you outsource this service, especially at a large scale.
%
%One reason why increasing engagement sounds like a good idea is because current democratic systems have two
%questionable assumptions: participants have time to participate, and knowledge to participate.
%If you do not participate it is your fault.
%Moreover, the legitimacy of decisions is based on participation as well.
%This is why those participating in the these democratic systems have motivation to try to increase participation
%of others (especially if they believe they will still be in majority), or claim they are at fault to not participate.
%
%engagement is then increased only to assure that people like the results
%
%so if we try to minimize engagement, but still make sure that people like the results, then this is the perfect system
%
%and only in the case when they are on the loosing side, then we have to make sure that they understand the reasons why
%they lost (e.g.,\ the middle panel in our design) or at least to feel that they participated, in at least some way
%(voting, or just delegating)
%
%but the participation is the last on this list of important factors
%
%the more important thing is that they understand why others were thinking differently
%or that they do not even have to be engaged
%
%we want that people do not have to pay attention to what government is doing
%
%currently, we are in a loop where we have a useless feedback loop, where government in fact would like for people
%to pay some type of attention because they need to be elected, so they have to show like they are doing something,
%but on the other hand they do not want too much engagement, because they do not have things in place to really
%engage with everyone
%
%government should be like infrastructure, you should not have to care about it while it works, and be there to fix
%things if it starts failing, but not even you personally, but have mechanisms and processes in place to find this
%
%Terminology:
%\begin{itemize}
%\item community -- group which is making a decision using PeerMind
%\item member -- user of the app who is participating in decision making
%\end{itemize}
%
%\todo[inline]{Terminology: decision vs. vote vs. voting (how to name the step in decision making where you vote, and what is what you cast?)}
%\todo[inline]{Terminology: motion? Tally? What is the sum of all votes?}
%\todo[inline]{Terminology: discarding a vote if you didn't vote and didn't delegate. Some other term?}
%
%The main question is: can we increase legitimacy and decrease attention required at the same time.
%Many others are trying to increase attention (participation) because they want to increase legitimacy,
%assuming that this is the only way.
%
%A list of potential other points:
%\begin{itemize}
%\item legitimacy (quorum, involvement of more people through delegation)
%\item scaling (delegation helps, less attention helps)
%\item attention (at same or better decisions)
%\item bad assumptions for democracy - time, knowledge, it is rational to know that you do not know, common practice is to ask friends
%\item better decisions (more people consulted, attention directed where it should be)
%\end{itemize}
%
%Another question: should feedback be visible (to see how others voted before you voted)?
%People go with majority.
%Better for wisdom of crowds is an independent sample.
%Maybe we should only allow how other voted to be seen after you voted (but you can still change the vote),
%but we could then observe that and learn from this and see if this is good or bad.
%Or we could just store information if you observed existing votes before you voted (you have to click a button to see them).
%Maybe going with majority is also good when you want more social cohesion in the community and not so much ``optimal''
%wisdom of crowds result -  you would want that people relax their positions based on how other people care.
%Cohesion of the group vs. accuracy.
%Maybe display only number of votes and credibility, maybe credibility direction or graph, but not average votes.
%
%A list of potential questions:
%\begin{itemize}
%\item Delegation works?
%\item Statistical quorum works?
%\item Real-time feedback influences?
%\item Private vs. public delegation (do you know how member to whom you delegated is voting)?
%\item When delegating, how to assure that you cannot learn how somebody else voted, but that you can still somehow
%learn how your vote is used?
%\item Knowing how much power you have vs. not knowing -- does it change how people behave? (Knowing might corrupt you,
%but also motivate you to do more thorough work voting because you know other depend on you.)
%\end{itemize}
%
%Performance/theory/scaling in computational terms (how big could effectively community can be to be able to compute it).
%Some other theoretical properties?
%Computing statistical quorum is an ``embarrassingly parallel'' problem, and so its
%use would not suffer in large populations.
%Sparsity of delegation matrix also enables use of (recently developed?)
%efficient matrix computation algorithms.
%
%Out of scope of this work:
%
%\begin{itemize}
%\item How to assure privacy of the delegation network (it is highly sensitive data, probably even more than votes)?
%\item How to compute delegation results in a way that it does not require access to the whole network of delegation at once?
%\item How can we make this system distributed (and still assure privacy)?
%\end{itemize}
%
%\section{Related work}
%
%\cite{andersen2008trust, dirnstorfer2010voting, ford2002delegative, rodriguez2007smartocracy, yamakawa2007toward}

@@

\subsection{Range Voting}

Range voting (score voting) is voting where members of a community express their positions on open proposals by assigning
each a score on a fixed scale, in the context of this paper, between $-1$ and $+1$.
Prior work has shown that this approach generalizes many previous approaches to voting and allows members to express their
positions in a highly informative and precise manner.
We find it especially suitable for a web application because many web users are used to use it when ranking products
and giving other ``five-star'' feedback.
Moreover, if later on a new proposal is added to a set of existing proposals on which voting was already open, only the
new proposal needs to be evaluated by members, as opposed to alternative voting systems where the relative rankings of
each proposal would need reassessing (assuming members use a consistent personal scale when voting).

\subsection{Dynamic Quorum}

\subsubsection{Background}
A population of voters (a community) needs to collectively decide which item (if any) to take action on out of a set of competing items.
In order to democratically take action, the population needs to have a \{simple, super\}-majority of ``yes'' votes on a
winning item, while also demonstrating that the winning item is preferred over all other competing items.
We do not want to poll the entire population, but we do want to be certain (specifically, $99\%$ certain) that
the population does not take undesired actions, which in this case encompasses taking action on an item that is not
supported by a majority of the population and/or taking action on an item that is not clearly preferred over all
other competing alternatives.

\subsubsection{Problem Statement}
We wish to compute the probability that the bias in a population towards voting ``yes'' is greater than some
fraction of the population (e.g., $50\%$ for a simple majority, $67\%$ for a super majority, $90\%$ for a consensus).
In addition, we wish to compute the probability that the bias towards voting ``yes'' on a specific item is greater
than the bias towards voting ``yes'' on all other competing items.

\subsubsection{Assumptions}
We assume that there is a fixed underlying bias in the population that is to be estimated given raw voting data.

@@

\subsubsection{Voting}
We allow for score voting where each member of the population may choose any real number in the range $[-1,+1]$ to
represent their vote, with $-1$ representing opposition and $+1$ representing support.
In the theory subsection below, we rescale votes to be in the range $[0,1]$ via the notation $\frac{votes + 1}{2}$.

@@

\subsubsection{Bayesian Theory}
To properly understand the Bayesian approach to parameter estimation, read the following instructive tutorial:
\url{http://www.behind-the-enemy-lines.com/2008/01/are-you-bayesian-or-frequentist-or.html}

@@

Hence, we have
\begin{align}\label{eq2}
& \Pr(\alpha^*_1 > T_1 \mid X_1) = \nonumber\\
& 1 - \int_0^1 \sum\limits_{i=0}^{V_1} {K_1 \choose i} p_1^{K_1-i} {(1-p_1)}^{i} \times \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \mathrm{d}p_1
\end{align}

@@

%\todo[inline]{Do we take into the account the distribution of votes? So if you have a very large standard deviation
%we might want to prefer a decision less than some other decision with smaller standard deviation, but maybe
%also smaller (but still positive) average. Is distribution of votes influencing dynamic quorum?}

@@

%\subsection{Three step process}
%
%\subsection{Real-time feedback}
%
%
%% Real-time communication in general.
%
%\subsection{Integration with offline meetings}
%
%Decoupling the information presentation and voting processes from the debating process in the full decision-making
%pipeline (with the idea being that debating is best done in person, and presenting information/voting is best done online).
%
%\section{Evaluation}
%
%\subsection{Design}
%
%User study/evaluation design.
%To create a controlled evaluation of our solutions, to not depend on general usage of our system among communities,
%we can evaluate the design with the following user study:
%\begin{enumerate}
%\item we find a tight community of around 100 people willing to participate in the user study
%\item they should know each other well (to know how to delegate)
%\item we offer them to pay some Amazon credits or something for participation
%\item every member of the community should define delegations
%\item we ask them to split into two groups, group A and group B
%\item group A (target size is around 20% of the community) will meet together or online and discuss various topics through our system
%\item discussed topics some can be completely random, to get people to be familiar with they system, and also have some
%easy topics to decide on, like, what ``should be the color of the sky if we could change it'', and some topics which are relevant to the community
%\item those discussions would be just for evaluation, but community can use the results in any way they find useful
%\item after this discussions and decisions were done we ask everyone from group B to evaluate the results, we present them with two results (blinded, them not knowing which was made in which way)
%\begin{itemize}
%\item results which would be obtained using traditional methods (majority voting without any our improvements)
%\item our results using our system
%\end{itemize}
%\item we ask them to evaluate which one (or both, or none) of decisions they agree with
%\item prediction is that members who have not participated in the decision making process will
%find decisions made through our system more often agreeable
%\item hypothesis here is that what a decision making system is trying to achieve is to find a decision most of the
%whole community can agree with, or like it, even when not everyone participates and not all information is available
%on their positions on a topic
%\end{enumerate}
%
%One additional part of the experimental delegation study:
%
%Compute statistical quorum with and without delegations.
%This semester, do not actually allow delegation to be used for passing statistical quorum, but collect data so that
%we can see how much earlier delegation reached quorum before official statistical quorum.
%(Only count how much earlier at the point where delegation passed quorum and never went below thereafter, thus
%showing the point where the decision truly was clear.)
%
%Evaluation of statistical quorum (given that we don't officially decide by including delegation this semester):
%From email: ``Do an internal Cloyne comparison that is more mathematical, showing how many agenda items were decided
%using fewer actual votes than old 33\% quorum, as a result of statistical quorum.
%This could be measured by average \# votes needed to pass statistical quorum vs. \% of those items that get
%formally passed at council via consent agenda.
%(If it's 100\%, then you can say that we saved X\% of votes on
%average by using our online voting).
%Then you could also show that some items needed more than 33\% of votes, implying that a hard-line 33\% is also bad.'' 
%
%Subjective evaluation of entire platform: Council Surveys comparing past two semesters to this semester for other
%houses vs. Cloyne.
%``use the previous 2 semesters' worth of council surveys as control, and a council survey for
%Cloyne at the end of this semester as results.
%These results would speak to those specific subjective questions
%and would be one useful thing to look at.''
%
%\bibliographystyle{sigchi}
%\bibliography{refs}
%
%More:
%\begin{itemize}
%\item https://mason.gmu.edu/~rhanson/futarchy.html
%\item http://merkle.com/papers/DAOdemocracyDraft.pdf
%\end{itemize}

>>>>

\title{PeerMind}

@@

The broad idea is that instead of just trying to move the voting process online -- something many others do -- we in
fact add additional value by voting online.
Specifically, we can compute results faster and more accurately, we can use sophisticated statistics to estimate
quantities for the entire voting population, and we can promote clarity and full understanding of the voting items for all.

\todo[inline]{Main questions and answers follow.}

What problem are we solving? Why is it important to solve? What is the story?

Finding a way to lower attention required but increase legitimacy of democratic decisions.
Traditionally legitimacy is increased by increasing participation/attention required.
It is an everlasting problem.
How to outsource governance and at the same time assure it does not get corrupt
or tyrannic.

Has anyone else tried to solve it or related problems? How did they try
and what were the results (subjective or objective)?

Described here: \url{http://mitar.tnode.com/post/73983101095/peer-to-peer-voting-scheme}.
Some tried delegations, but mostly only to one person.
Getting issues that you have tree-structure with possible cycles you cannot resolve.
Often there were reported UI problems as well.
So just technically improving is not enough, you also have to have UI for the technical solution so that people can trust.

How are you solving the problem? What technologies are you using?

Using dynamic quorum, score voting, delegation, and nice integration with UI/UX.

How will you know how well you solved the problem? How will those technologies address the issues?

If it improves decision making, participation, inclusivity, activity of people engaged in decision making in my house.
So currently we have issues with reaching the quorum and many people do not participate.
I would like for them to have easier time participating (less time required) and as a consequence more people to
participate collectively.
If I observe that I think I will know I solved the problem.

\todo[inline]{This rest of the section is mostly notes. Organize and improve.}

We can often hear that the issue of our democracy is low engagement.
But this is a fallacy, because we should be instead trying to decrease engagement.
The best governance system is one where you do not have to be involved yourself, but it is still doing things
like you would like to do them.
% Or even, doing things you might not even know that you would like to be done, especially in a long term.
We want to outsource the job of coordination between people.
Sometimes you want to coordinate people yourself (in your company, team), you might enjoy it, but in most cases
you cannot or do not want to, so you outsource this service, especially at a large scale.

One reason why increasing engagement sounds like a good idea is because current democratic systems have two
questionable assumptions: participants have time to participate, and knowledge to participate.
If you do not participate it is your fault.
Moreover, the legitimacy of decisions is based on participation as well.
This is why those participating in the these democratic systems have motivation to try to increase participation
of others (especially if they believe they will still be in majority), or claim they are at fault to not participate.

engagement is then increased only to assure that people like the results

so if we try to minimize engagement, but still make sure that people like the results, then this is the perfect system

and only in the case when they are on the loosing side, then we have to make sure that they understand the reasons why
they lost (e.g.,\ the middle panel in our design) or at least to feel that they participated, in at least some way
(voting, or just delegating)

but the participation is the last on this list of important factors

the more important thing is that they understand why others were thinking differently
or that they do not even have to be engaged

we want that people do not have to pay attention to what government is doing

currently, we are in a loop where we have a useless feedback loop, where government in fact would like for people
to pay some type of attention because they need to be elected, so they have to show like they are doing something,
but on the other hand they do not want too much engagement, because they do not have things in place to really
engage with everyone

government should be like infrastructure, you should not have to care about it while it works, and be there to fix
things if it starts failing, but not even you personally, but have mechanisms and processes in place to find this

Terminology:
\begin{itemize}
\item community -- group which is making a decision using PeerMind
\item member -- user of the app who is participating in decision making
\end{itemize}

\todo[inline]{Terminology: decision vs. vote vs. voting (how to name the step in decision making where you vote, and what is what you cast?)}
\todo[inline]{Terminology: motion? Tally? What is the sum of all votes?}
\todo[inline]{Terminology: discarding a vote if you didn't vote and didn't delegate. Some other term?}

The main question is: can we increase legitimacy and decrease attention required at the same time.
Many others are trying to increase attention (participation) because they want to increase legitimacy,
assuming that this is the only way.

A list of potential other points:
\begin{itemize}
\item legitimacy (quorum, involvement of more people through delegation)
\item scaling (delegation helps, less attention helps)
\item attention (at same or better decisions)
\item bad assumptions for democracy - time, knowledge, it is rational to know that you do not know, common practice is to ask friends
\item better decisions (more people consulted, attention directed where it should be)
\end{itemize}

Another question: should feedback be visible (to see how others voted before you voted)?
People go with majority.
Better for wisdom of crowds is an independent sample.
Maybe we should only allow how other voted to be seen after you voted (but you can still change the vote),
but we could then observe that and learn from this and see if this is good or bad.
Or we could just store information if you observed existing votes before you voted (you have to click a button to see them).
Maybe going with majority is also good when you want more social cohesion in the community and not so much ``optimal''
wisdom of crowds result -  you would want that people relax their positions based on how other people care.
Cohesion of the group vs. accuracy.
Maybe display only number of votes and credibility, maybe credibility direction or graph, but not average votes.

A list of potential questions:
\begin{itemize}
\item Delegation works?
\item Statistical quorum works?
\item Real-time feedback influences?
\item Private vs. public delegation (do you know how member to whom you delegated is voting)?
\item When delegating, how to assure that you cannot learn how somebody else voted, but that you can still somehow
learn how your vote is used?
\item Knowing how much power you have vs. not knowing -- does it change how people behave? (Knowing might corrupt you,
but also motivate you to do more thorough work voting because you know other depend on you.)
\end{itemize}

Performance/theory/scaling in computational terms (how big could effectively community can be to be able to compute it).
Some other theoretical properties?
Computing statistical quorum is an ``embarrassingly parallel'' problem, and so its
use would not suffer in large populations.
Sparsity of delegation matrix also enables use of (recently developed?)
efficient matrix computation algorithms.

Out of scope of this work:

\begin{itemize}
\item How to assure privacy of the delegation network (it is highly sensitive data, probably even more than votes)?
\item How to compute delegation results in a way that it does not require access to the whole network of delegation at once?
\item How can we make this system distributed (and still assure privacy)?
\end{itemize}

\section{Related work}

\cite{andersen2008trust, dirnstorfer2010voting, ford2002delegative, rodriguez2007smartocracy, yamakawa2007toward}

@@

\subsection{Statistical Quorum}

\subsubsection*{Background}
A population of voters needs to collectively decide which item (if any) to take action on out of a set of competing items.  In order to democratically take action, the population needs to have a \{simple, super\}-majority of ``yes'' votes on a winning item, while also demonstrating that the winning item is preferred over all other competing items.  We do not want to poll the entire population, but we do want to be certain (specifically, $99\%$ certain) that the population does not take undesired actions, which in this case encompasses taking action on an item that is not supported by a majority of the population and/or taking action on an item that is not clearly preferred over all other competing alternatives.

\subsubsection*{Problem Statement}
We wish to compute the probability that the bias in a population towards voting ``yes'' is greater than some fraction of the population (e.g., $50\%$ for a simple majority, $67\%$ for a super majority, $90\%$ for a consensus).  In addition, we wish to compute the probability that the bias towards voting ``yes'' on a specific item is greater than the bias towards voting ``yes'' on all other competing items.

\subsubsection*{Assumptions}
We assume that there is a fixed underlying bias in the population that is to be estimated given raw voting data.

@@

\subsubsection*{Voting}
We allow for score voting where each member of the population may choose any real number in the range $[-1,+1]$ to represent their vote, with $-1$ representing opposition and $+1$ representing support.  In the theory subsection below, we rescale votes to be in the range $[0,1]$ via the notation $\frac{votes + 1}{2}$.

@@

\subsubsection*{Bayesian Theory}
To properly understand the Bayesian approach to parameter estimation, read the following instructive tutorial: \url{http://www.behind-the-enemy-lines.com/2008/01/are-you-bayesian-or-frequentist-or.html}

@@

Hence, we have
\begin{align}\label{eq2}
& \Pr(\alpha^*_1 > T_1 \mid X_1) = \nonumber\\
& 1 - \int_0^1 \sum\limits_{i=0}^{V_1} {K_1 \choose i} p_1^{K_1-i} {(1-p_1)}^{i} \cdot \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \mathrm{d}p_1
\end{align}

@@

\subsection{Score Voting}

\todo[inline]{Do we take into the account the distribution of votes? So if you have a very large standard deviation
we might want to prefer a decision less than some other decision with smaller standard deviation, but maybe
also smaller (but still positive) average. Is distribution of votes influencing dynamic quorum?}

@@

\subsection{Three step process}

\subsection{Real-time feedback}

% Real-time communication in general.

\subsection{Integration with offline meetings}

Decoupling the information presentation and voting processes from the debating process in the full decision-making
pipeline (with the idea being that debating is best done in person, and presenting information/voting is best done online).

\section{Evaluation}

\subsection{Design}

User study/evaluation design.
To create a controlled evaluation of our solutions, to not depend on general usage of our system among communities,
we can evaluate the design with the following user study:
\begin{enumerate}
\item we find a tight community of around 100 people willing to participate in the user study
\item they should know each other well (to know how to delegate)
\item we offer them to pay some Amazon credits or something for participation
\item every member of the community should define delegations
\item we ask them to split into two groups, group A and group B
\item group A (target size is around 20% of the community) will meet together or online and discuss various topics through our system
\item discussed topics some can be completely random, to get people to be familiar with they system, and also have some
easy topics to decide on, like, what ``should be the color of the sky if we could change it'', and some topics which are relevant to the community
\item those discussions would be just for evaluation, but community can use the results in any way they find useful
\item after this discussions and decisions were done we ask everyone from group B to evaluate the results, we present them with two results (blinded, them not knowing which was made in which way)
\begin{itemize}
\item results which would be obtained using traditional methods (majority voting without any our improvements)
\item our results using our system
\end{itemize}
\item we ask them to evaluate which one (or both, or none) of decisions they agree with
\item prediction is that members who have not participated in the decision making process will
find decisions made through our system more often agreeable
\item hypothesis here is that what a decision making system is trying to achieve is to find a decision most of the
whole community can agree with, or like it, even when not everyone participates and not all information is available
on their positions on a topic
\end{enumerate}

One additional part of the experimental delegation study:

Compute statistical quorum with and without delegations.
This semester, do not actually allow delegation to be used for passing statistical quorum, but collect data so that
we can see how much earlier delegation reached quorum before official statistical quorum.
(Only count how much earlier at the point where delegation passed quorum and never went below thereafter, thus
showing the point where the decision truly was clear.)

Evaluation of statistical quorum (given that we don't officially decide by including delegation this semester):
From email: ``Do an internal Cloyne comparison that is more mathematical, showing how many agenda items were decided
using fewer actual votes than old 33\% quorum, as a result of statistical quorum.
This could be measured by average \# votes needed to pass statistical quorum vs. \% of those items that get
formally passed at council via consent agenda.
(If it's 100\%, then you can say that we saved X\% of votes on
average by using our online voting).
Then you could also show that some items needed more than 33\% of votes, implying that a hard-line 33\% is also bad.''

Subjective evaluation of entire platform: Council Surveys comparing past two semesters to this semester for other
houses vs. Cloyne.
``use the previous 2 semesters' worth of council surveys as control, and a council survey for
Cloyne at the end of this semester as results.
These results would speak to those specific subjective questions
and would be one useful thing to look at.''

\bibliographystyle{sigchi}
\bibliography{refs}

More:
\begin{itemize}
\item https://mason.gmu.edu/~rhanson/futarchy.html
\item http://merkle.com/papers/DAOdemocracyDraft.pdf
\end{itemize}
